Understanding domestic abuse

### 2019-07-23 JeS_fields.tex
Anna update

Ultimately, the fundamental goal of this research project is to benefit victims of domestic abuse by improving their safety. We aim to do so by working together other stakeholders, including the police, charities, and the government.

>>>>

Ultimately, the fundamental goal of this research project is to benefit victims of domestic abuse. We aim to do so by expanding the knowledge of other stakeholders, including the police, charities, and the government.

### 2019-07-23 pathways_to_impact.tex
Anna update

The research proposed here has been developed with direct input from officers and experts within WMP. This has allowed us to design the research questions that are relevant to current issues within WMP, and that can feed in to existing structures to accellerate the dissemination of findings, and changes in policy. To facilitate this, we have a day-to-day contact at West Midlands Police: Inspector Jenny Richards (Evidence Based Practice in Risk and Organisational Learning), and within the West Midlands Police and Crime Commissioner's Office: Alison Spence. As aresult of this close collaboration, we have received support from senior levels within WMP including from Deputy Chief Constable Louisa Rolfe who is the National Police Chiefs Council lead for domestic abuse.

These relationships will enable us to work with West Midlands Police to import the insight from the research into their senior management team and also their day-to-day processes. This will be possible for each of the objectives and topics within our proposal:

@@

2. The programme on the  ``decision to report'' links with police's design of the inital contact with victims (e.g., https://west-midlands.police.uk/your-options/domestic-abuse). It will also help the police to develop more efficient and targetted intervention and awareness campaigns.

@@

4. The programme on ``envionmental factors influencing abuse'' can be used to help predict which local populations are most at risk of abuse in the West Midlands. It can also give clues as to likely triggering events, such as economic shocks, or changes to benefits, and large events such as sports championships.

In addition to workign with WMP, our links to the National Police Chiefs council, and collaboration with the College of Policing, provide pathways for impact accross all forces. At the College of Policing (situated just a few miles from Warwick campus) we will work within the framework of the \href{https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/) and the revision of the existing DASH risk assessment tool for domestic abuse. (https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf}{Authorised Professional Practice} on domestic abuse, released in 2015. We will work initially with David Tucker, Head Crime and Criminal Justice at the College of Policing.

We will meet regularly with our contacts at WMP and the college of policing througout the grant. This will enable us to adapt to current questions that arise during the period of the proposal. It also allows us to react quickly to any unaticipated issues that arise as a result of our findings, such as following up on unexpected results to identify underlying causes. It also ensures that there is an ongoing dialogue about the data being used, and provides an opportunity to alert the police to any data quality issues.

In the second year of the proposal we will hold a 1-day impact summit at Warwick Business School's London Shard venue. This will be funded by the Warwick Business School Impact Fund, and potentially the ESRC Impact Accelleration Account. We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at West Midlands Police), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry. The summit will be a 50/50 academic / practitioner mix. We will contact, early in the project, [Insert list of charities in this sector] and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.

@@

Within Lloyds Bank, we will work with Martin King, Head of Customer Vulnerability. Warwick already has a relationship with King's team in CI Stewart's work on the effects of gambling, which was completed using micro-level transaction data from millions of account holders. Key issues here are work on coercion and control, and having sufficient financial resiliance to escape an abusive relationship and being able to make the decision to report an abuser. Our day-to-day contact at Lloyds is Dr David Leake, Head of the Behavioural Insights Team. We will present the findings from all four programmes to the Lloyds Vulnerability Team in six-monthly briefings, and work to integrate insight from the research into the Lloyds environment.

>>>>

The research proposed here has been developed with direct input from officers and experts within WMP. This has allowed us to design the research questions that are relevant to current issues within WMP, and that can feed in to existing structures to accelerate the dissemination of findings, and changes in policy. To facilitate this, we have a day-to-day contact at WMP: Inspector Jenny Richards (Evidence Based Practice in Risk and Organisational Learning), and within the West Midlands Police and Crime Commissioner's Office, Alison Spence. As a result of this close collaboration, we have received support from senior levels within WMP including from Deputy Chief Constable Louisa Rolfe who is the National Police Chiefs Council lead for domestic abuse.

These relationships will enable us to work with WMP to import the insight from the research into their senior management team and also their day-to-day processes. This will be possible for each of the objectives and topics within our proposal:

@@

2. The programme on the  ``decision to report'' links with police's design of the initial contact with victims (e.g., https://west-midlands.police.uk/your-options/domestic-abuse). It will also help the police to develop more efficient and targeted intervention and awareness campaigns.

@@

4. The programme on ``environmental factors influencing abuse'' can be used to help predict which local populations are most at risk of abuse in the West Midlands. It can also give clues as to likely triggering events, such as economic shocks, or changes to benefits, and large events such as sports championships.

In addition to working with WMP, our links to the National Police Chiefs council, and collaboration with the College of Policing, provide pathways for impact across all forces. At the College of Policing (situated just a few miles from Warwick campus) we will work within the framework of the \href{https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/) and the revision of the existing DASH risk assessment tool for domestic abuse. (https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf}{Authorised Professional Practice} on domestic abuse, released in 2015. We will work initially with David Tucker, Head Crime and Criminal Justice at the College of Policing.

We will meet regularly with our contacts at WMP and the college of policing throughout the grant. This will enable us to adapt to current questions that arise during the period of the proposal. It also allows us to react quickly to any unanticipated issues that arise as a result of our findings, such as following up on unexpected results to identify underlying causes. It also ensures that there is an ongoing dialogue about the data being used, and provides an opportunity to alert the police to any data quality issues.

In the second year of the proposal we will hold a 1-day impact summit at Warwick Business School's London Shard venue. This will be funded by the Warwick Business School Impact Fund, and potentially the ESRC Impact Acceleration Account. We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at West Midlands Police), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry. The summit will be a 50/50 academic / practitioner mix. We will contact, early in the project, [Insert list of charities in this sector, Women's Aid, Refuge, Safe Lives, National Centre for Domestic Abuse] and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.

@@

Within Lloyds Bank, we will work with Martin King, Head of Customer Vulnerability. Warwick already has a relationship with King's team in CI Stewart's work on the effects of gambling, which was completed using micro-level transaction data from millions of account holders. Key issues here are work on coercion and control, and having sufficient financial resilience to escape an abusive relationship and being able to make the decision to report an abuser. Our day-to-day contact at Lloyds is Dr David Leake, Head of the Behavioural Insights Team. We will present the findings from all four programmes to the Lloyds Vulnerability Team in six-monthly briefings, and work to integrate insight from the research into the Lloyds environment.
